\plaintitle

### 2018-04-04 paper/paper.tex
...

@@

% Copyright
\CopyrightYear{2016}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{UIST'18,}{May 07--12, 2016, San Jose, CA, USA}
%Price
\acmPrice{\$15.00}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\sf#1{\textsf{#1}}
\long\def\qtt#1{``\texttt{#1}''}
\long\def\qsf#1{``\textsf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to a machine from
  the user's vague intention
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

There have been tremendous amount of researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people.
Information on the net is really rich these days, and we can easily
find somebody who can answer questions intelligently.
This is a very good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like ExpandHelp is
preferable before asking other people.

@@

Text input systems for non-English languages are used widely in the world, and
they are called as ``input methods'' (IMs).

@@

Many research and development on IMs have been performed for years, and
people are using them all the time for entering text in their mother language.

IMs are a kind of translation system that convert one
expression (pronunciation, etc.) into a textual form of a language.
In the above example, ``kanji'' will be translated to ``漢字''.

IMs are very popular especially in South-East Asian countries, and
it is very common for people there to 
use translation systems for using computers.

@@

On text editors an│shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \qtt{la} on the Unix shell,
\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
When a user types \qtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \tt{README.md} file, and
replace the user's input with \qtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been adopted in text editors and command line editors.

User's history data can be used for 
The Reactive Keyboard system\cite{ReactiveKeyboard}
accumlates the user's command history and use the data
for predicting the user's next command.
Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.

Gitsome(https://github.com/donnemartin/gitsome)
helps \tt{git} users by dynamically
showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

@@

Many smart IDEs for suggesting codes are proposed.

賢い補完
\cite{Little:2006:TKC:1166253.1166275}
% キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
% キーワードぐらいは思い出せるプログラマが対象になっている
% 「margin」とか「left」とかいう単語は思い出す必要がある
% 「ちょっと字下げ」とか言っても駄目
% キーワードが違ってると駄目?
% いろいろズルをしてるようだ
% [[ActiveDocument]]はよく出てくるので特別扱いしているとか
% ステミングをしている
% ``the'' ``to'' などは捨ててるのだろう
% そもそもリカーシブな検索アルゴリズムにかなり無理がありそう
% テンプレートを作るのは大変ではないのか?

AnyCode\cite{Gvero:2015:SJE:2814270.2814295}
% [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
% [[copy fileA fileB]]みたいなキーワードから[[FileUtil.copyFile(new File(fileA), new File(fileB))]]みたいなコード候補を生成する
% [自然言語処理]を行なっている
% [https://github.com/tihomirg/nlpcoder/tree/noola GitHub]
% 曖昧検索はできない
% 真面目に自然言語を入れる必要がある
% `123`みたいなパラメタは使えるか?
% 使えると思うが例には出てこない
% コードの説明文は出ない?
% FileUtil.copyFile(new File(fileA), new File(fileB)) と言われても、どちらが新しいファイルなのかわからない

Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
% [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
% `getDefaultColor()` を定義したいとき`purple`と入力すると、それに対応した候補が提示されるとか
% 普段使ってる環境で有益な候補が表示されると嬉しいだろうと言っている
% [[コメント]]
% [Jun Kato.icon]
% > Active code completionも思い出しました。型ごとに適した入力インタフェースを出すコード補完インタフェースのnn提案です。確か。
% [増井俊之.icon]
% IDEでどういう機能が欲しいかサーベイして設計したことになっている
% 色選択と正規表現のためのコード生成をサポートした例が紹介されている
% 一般的な補完コマンド起動によって呼び出されるようだ
% サポートウィンドウはHTML5で生成する
% しかし両者とも[/palette]の作成はかなり大変である
% 普通のユーザが作れるようなものではない
% [* 作成がすごく大変]で、[* 特定のIDEでしか使えない]という問題があると思う

Code Completion from Abbreviated\cite{Han:2009:CCA:1747491.1747530}
% [HMM]を使って正しいコードを予測して提示する
% `ch opn`みたいなテキトーな入力から`chooser.showOpenDialog()`みたいな正しいコードが候補に出る
% コードデータベースを解析
% [[コメント]]
% [増井俊之.icon] 2018/3/23 18:53
% コードのほんの一部を指定すると正しく予測されるというのは面白い
% HMMってそういうのに使えるのね
% しかし[* 関数名とか全然覚えていないときは使えないだろう]
% [語彙問題]が解決できてない
% だとすると高速入力の役にはたつが、何もかもわからない人をサポートはできない
% 用例データが存在しない場合も使えない
% [IDE]でしか使えない
% [Cyrus Omar: Active code completion]で参照されている

\subsection{Using cloud data for development}
% 他人の情報利用する系
% コード共有、コンパイルエラー共有

BluePrint \cite{Brandt:2010:EPI:1753326.1753402}
%   サンプルコードをすぐ参照して利用できる[IDE]

Bjorn\cite{Hartmann:2010:OPS:1753326.1753478}
% 他人のヒストリを使ってコンパイルエラー対処法をサジェスト

\subsection{Using user forums}

% Qiita, StackOverflow

>>>>

% compare current (README.md|index.html) with the file from 2 versions ago
% compare (README.md|index.html) with the one from (1|2|3|4) versions before
% compare current (README.md|index.html) with that from  ([0-9]+)-days ago

@@

% Copyright
\CopyrightYear{2018}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{UIST'18,}{May 07--12, 2016, San Jose, CA, USA}
%Price
\acmPrice{\$15.00}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\small{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\small{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to a machine from
  the user's vague intention
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item IME-like command etnry interface
% やりたいことを実行するインタフェース (IME的なもの)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

There have been many researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people,
either by searching Web pages or 
by asking in user forums like StackOverflow\footnote{stackoverflow}.
Information on the net is rich these days, and we can easily
find somebody who can answer questions intelligently.
This is a good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like {\EH} is
preferable before asking other people.

@@

Text input systems for non-English languages are widely used
in the world,
and they are called as ``Input Methods'' (IMs).
%
Many research and development on IMs have been going on for years, and
people are using them every day for entering texts in their mother language.

@@

IMs are one form of translation systems that convert one
expression (pronunciation, character shape, etc.)
into a textual form of a language.
In the above example, the pronunciation ``kanji''
is used for getting ``漢字''.

IMs are very popular in the world these days,
and it is very common for people to 
use translation systems for using computers.
Using an additional translation system like {\GH} is ...

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \qtt{la} on the Unix shell,
\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
When a user types \qtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \tt{README.md} file, and
replace the user's input with \qtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in text editors and command line editors.

User's history data can also be used for the completion function.
The Reactive Keyboard\cite{ReactiveKeyboard}
accumlates the user's command history and use the data
for predicting the user's next input.

% Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps \tt{git} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

@@

Many smart IDEs for suggesting codes have been proposed resently.

% 賢い補完
Little's system\cite{Little:2006:TKC:1166253.1166275}
generates a complete JavaScript code snippet from keyword fragments.
For example,
\qtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
can be generated from keywords like
\qsf{left},
\qsf{margin},
\qsf{4}, and
\qsf{inches}.
The system generates the code using a template database and heuristics
for the target system.
It is useful for a special environment, but
users of the system cannot modify the algorithm or the database
even when appropriate suggestions cannot be give by the system.

% キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
% キーワードぐらいは思い出せるプログラマが対象になっている
% 「margin」とか「left」とかいう単語は思い出す必要がある
% 「ちょっと字下げ」とか言っても駄目
% キーワードが違ってると駄目?
% いろいろズルをしてるようだ
% [[ActiveDocument]]はよく出てくるので特別扱いしているとか
% ステミングをしている
% ``the'' ``to'' などは捨ててるのだろう
% そもそもリカーシブな検索アルゴリズムにかなり無理がありそう
% テンプレートを作るのは大変ではないのか?

% https://www.youtube.com/watch?v=93vZAmLyOQY
AnyCode\cite{Gvero:2015:SJE:2814270.2814295} is another system
that generates a complete code snippet from the user's
input in natural language.
AnyCode can handle synonyms like ``make'' == ``create'',
曖昧検索はできず、かなりキーワードを指定する必要はある

% [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
% [[copy fileA fileB]]みたいなキーワードから[[FileUtil.copyFile(new File(fileA), new File(fileB))]]みたいなコード候補を生成する
% [自然言語処理]を行なっている
% [https://github.com/tihomirg/nlpcoder/tree/noola GitHub]
% 曖昧検索はできない
% 真面目に自然言語を入れる必要がある
% `123`みたいなパラメタは使えるか?
% 使えると思うが例には出てこない
% コードの説明文は出ない?
% FileUtil.copyFile(new File(fileA), new File(fileB)) と言われても、どちらが新しいファイルなのかわからない

Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
is another code completion system for the Eclipse IDE.
A database called \textit{palette} are used for code completion and coding support
for Java classes.
When a user wants to write a code for drawing a rectangle in purple,
the user should just tell ``purple'' to the system,
and the system shows the user a color selection window
as well as the Java code for drawing a purple rectangle.
This is a useful feature for the user to write a code including selecting
a color, but paletts are difficult to create, and should be provided
as IDE plugins.
% [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
% `getDefaultColor()` を定義したいとき`purple`と入力すると、それに対応した候補が提示されるとか
% 普段使ってる環境で有益な候補が表示されると嬉しいだろうと言っている
% [[コメント]]
% [Jun Kato.icon]
% > Active code completionも思い出しました。型ごとに適した入力インタフェースを出すコード補完インタフェースのnn提案です。確か。
% [増井俊之.icon]
% IDEでどういう機能が欲しいかサーベイして設計したことになっている
% 色選択と正規表現のためのコード生成をサポートした例が紹介されている
% 一般的な補完コマンド起動によって呼び出されるようだ
% サポートウィンドウはHTML5で生成する
% しかし両者とも[/palette]の作成はかなり大変である
% 普通のユーザが作れるようなものではない
% [* 作成がすごく大変]で、[* 特定のIDEでしか使えない]という問題があると思う

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a snippet like \qtt{chooser. showOpenDialog()}
can be generated from the keyword
\qsf{ch} and\qsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \qtt{chooser}, \qtt{dialog}),
and large code example corpus should exist before

% [HMM]を使って正しいコードを予測して提示する
% `ch opn`みたいなテキトーな入力から`chooser.showOpenDialog()`みたいな正しいコードが候補に出る
% コードデータベースを解析
% [[コメント]]
% [増井俊之.icon] 2018/3/23 18:53
% コードのほんの一部を指定すると正しく予測されるというのは面白い
% HMMってそういうのに使えるのね
% しかし[* 関数名とか全然覚えていないときは使えないだろう]
% [語彙問題]が解決できてない
% だとすると高速入力の役にはたつが、何もかもわからない人をサポートはできない
% 用例データが存在しない場合も使えない
% [IDE]でしか使えない
% [Cyrus Omar: Active code completion]で参照されている

\subsection{Using cloud data for development}

% 他人の情報利用する系
% コード共有、コンパイルエラー共有

Many systems support sharing users' development experiences on the web so that
they can be used on the developers' IDE.

Using BluePrint\cite{Brandt:2010:EPI:1753326.1753402}
as a plugin for Adobe Flex Builder,
users can search sample codes from the Web and use it immediately
as

%   サンプルコードをすぐ参照して利用できる[IDE]

HelpMeOut\cite{Hartmann:2010:OPS:1753326.1753478} tells users
how to handle compile errors,
based on the people's experiences of handling compile errors.

%= 他人のヒストリを使ってコンパイルエラー対処法をサジェスト

% \subsection{Using user forums}
% 
% Qiita, StackOverflow
%
